### 2022-04-08 papers.tex
Final 2022 version??? Probably not

\addpaper
    {Edward, edMUnD \& Edwin: Line-Based Text Editing for the 21st Century}
    {Natalia Posting and Katie Wolfe}
    {Keywords: line-based text editing, line-cringe text editing, synergy}
    {SIGBOVIK_2022_paper_6729}
    {0cm}
    {}
\addpaper
    {Redundant Coupling}
    {Peter Kos}
    {Keywords: software engineering, coupling, cohesion, rust, martin fowler, fowler, james gosling, donald knuth}
    {SIGBOVIK_2022_paper_8888}
    {0cm}
    {}

@@

\addpaper
    {Towards Cloud Computing}
    {Alex Xie and Alan Hsu}
    {Keywords: cloud computing, deep learning, machine learning, computer vision, toddlers, kahoot, clout, drip, label smoothing, data science, animals, atmospheric sciences, meteorology}
    {SIGBOVIK_2022_paper_2551}
    {0cm}
    {}
\addpaper
    {Ecological Memory Management: Beyond Garbage Collection}
    {Erik Derohanian, Dann Toliver and Saul Field}
    {Keywords: Garbage Collection, Compost, Memory Management, Organic Computing}
    {SIGBOVIK_2022_paper_2558}
    {0cm}
    {}
\addpaper
    {Infrastructure-as-PowerPoint: A No-Code Approach to Cloud Infrastructure Management}
    {Tobias Pfandzelter}
    {Keywords: cloud computing, powerpoint, slideshow bob}
    {SIGBOVIK_2022_paper_3392}
    {0cm}
    {}

@@

\addtrack
    {}{Best Practices}
%\addpaper
%    {Investigations and Difficulties in Real - to -Sim}
%    {Sashank Tirumala}
%    {Keywords: Robotics, Machine Learning, Deep Learning, Reinforcement Learning}
%    {SIGBOVIK_2022_paper_3472}
%    {0cm}
%    {}
\addpaper
    {Quadruple-Blind Peer Review}
    {Yuriko Shu}
    {Keywords: Peer Review, Quadruple Blind Reviewing, Bias Reduction}
    {SIGBOVIK_2022_paper_3958}
    {0cm}
    {}
\addpaper
    {Optimal degeneracy through OwO based variable names}
    {Fwans Skawman}
    {Keywords: OwO, What's, This}
    {SIGBOVIK_2022_paper_4751}
    {0cm}
    {}

@@

\addpaper
    {Improved Data and Instruction Locality in Long Division}
    {Isaac Grosof, Isaac Grosof}
    {Keywords: performance, division, locality, data, instruction}
    {SIGBOVIK_2022_paper_0463}
    {0cm}
    {}

\addpaper
    {The New New Math: using sentiment analysis of mathematics word problems to gauge children's reactions to teaching 8-bit floating point arithmetic for the new California public school math curriculum}
    {Lee Butterman}
    {Keywords: education, early childhood education, won't someone think of the children, won't someone think of the chiiiiiiildren, new math, California math education guidelines, data science, calculus, graphics processing units, dozens of petaflops, sentiment analysis, numerology, fear of Arabic numerals, 8-bit floating point}
    {SIGBOVIK_2022_paper_4483}
    {0cm}
    {}

@@

\addpaper
    {Attractiveness Learning: A General Solution for the Cold-Start Problem}
    {Yajuan Gu and Yuxun Lu}
    {neural network, attractive mechanism, recommender system, cold-start problem}
    {SIGBOVIK_2022_paper_2018}
    {0cm}
    {}

\addtrack
    {}{Hardware}

@@

\addpaper
    {Wearable RF-shield repositories}
    {Abe Wits and J. Mijn}
    {Keywords: security, wifi, cable}
    {SIGBOVIK_2022_paper_9009}
    {0cm}
    {}
\addtrack
    {}{Black Boxes}

>>>>

\addpaper
    {Edward, edMUnD \& Edwin: Line-Based Text Editing for the 21st Century}
    {Natalia Posting and Katie Wolfe}
    {Keywords: line-based text editing, line-cringe text editing, synergy}
    {SIGBOVIK_2022_paper_6729}
    {0cm}
    {}
\addpaper
    {Redundant Coupling}
    {Peter Kos}
    {Keywords: software engineering, coupling, cohesion, rust, martin fowler, fowler, james gosling, donald knuth}
    {SIGBOVIK_2022_paper_8888}
    {0cm}
    {\badges{\badge{pagenumbers}}}

@@

\addpaper
    {Towards Cloud Computing}
    {Alex Xie and Alan Hsu}
    {Keywords: cloud computing, deep learning, machine learning, computer vision, toddlers, kahoot, clout, drip, label smoothing, data science, animals, atmospheric sciences, meteorology}
    {SIGBOVIK_2022_paper_2551}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addpaper
    {Ecological Memory Management: Beyond Garbage Collection}
    {Erik Derohanian, Dann Toliver and Saul Field}
    {Keywords: Garbage Collection, Compost, Memory Management, Organic Computing}
    {SIGBOVIK_2022_paper_2558}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addpaper
    {Infrastructure-as-PowerPoint: A No-Code Approach to Cloud Infrastructure Management}
    {Tobias Pfandzelter}
    {Keywords: cloud computing, powerpoint, slideshow bob}
    {SIGBOVIK_2022_paper_3392}
    {0cm}
    {}

@@

\addtrack
    {}{Best Practices}
%\addpaper
%    {Investigations and Difficulties in Real - to -Sim}
%    {Sashank Tirumala}
%    {Keywords: Robotics, Machine Learning, Deep Learning, Reinforcement Learning}
%    {SIGBOVIK_2022_paper_3472}
%    {0cm}
%    {}
\addpaper
    {Quadruple-Blind Peer Review}
    {Yuriko Shu}
    {Keywords: Peer Review, Quadruple Blind Reviewing, Bias Reduction}
    {SIGBOVIK_2022_paper_3958}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2022_review_3}
    {0cm}

\addpaper
    {Optimal degeneracy through OwO based variable names}
    {Fwans Skawman}
    {Keywords: OwO, What's, This}
    {SIGBOVIK_2022_paper_4751}
    {0cm}
    {\badges{\badge{pagenumbers}}}

@@

\addpaper
    {Improved Data and Instruction Locality in Long Division}
    {Isaac Grosof, Isaac Grosof}
    {Keywords: performance, division, locality, data, instruction}
    {SIGBOVIK_2022_paper_0463}
    {0cm}
    {\badges{\badge{pagenumbers}}}

\addpaper
    {The New New Math: using sentiment analysis of mathematics word problems to gauge children's reactions to teaching 8-bit floating point arithmetic for the new California public school math curriculum}
    {Lee Butterman}
    {Keywords: education, early childhood education, won't someone think of the children, won't someone think of the chiiiiiiildren, new math, California math education guidelines, data science, calculus, graphics processing units, dozens of petaflops, sentiment analysis, numerology, fear of Arabic numerals, 8-bit floating point}
    {SIGBOVIK_2022_paper_4483}
    {0cm}
    {\badges{\badge{pagenumbers}}}

@@

\addpaper
    {Attractiveness Learning: A General Solution for the Cold-Start Problem}
    {Yajuan Gu and Yuxun Lu}
    {neural network, attractive mechanism, recommender system, cold-start problem}
    {SIGBOVIK_2022_paper_2018}
    {0cm}
    {}
\addtrack
    {}{Hardware}

@@

\addpaper
    {Wearable RF-shield repositories}
    {Abe Wits and J. Mijn}
    {Keywords: security, wifi, cable}
    {SIGBOVIK_2022_paper_9009}
    {0cm}
    {\badges{\badge{pagenumbers}}}
\addtrack
    {}{Black Boxes}
